Kindly Bent to Free Us

### 2019-07-09 kindly/soa.tex
More SOA.

\subsection{Substructural type systems}

@@

\subsubsection{Functional languages}

@@

\subsubsection{Other systems}

@@

\lang strongly relies on qualified types~\cite{DBLP:journals/scp/Jones94}
to introduce the necessary kind equalities in our system. In
particular, we use HM(X)~\citep{DBLP:journals/tapos/OderskySW99} which
allow to use qualified type in an ML-like language with complete
type inference.
HM(X) has been shown to be compatible with subtyping,
bounded universal and existentials~\citep{DBLP:conf/icfp/Simonet03}
GADTs~\citep{DBLP:journals/toplas/SimonetP07},
and syntactic proof of soundness~\citep{DBLP:journals/entcs/SkalkaP02}.
This makes us confident that the system developed in \lang
could be applied to larger and more complex languages such as OCaml.

The subtyping discipline we develop in \lang is very similar
to structural subtyping, where the only subtyping (or here, subkinding)
is at the leafs.
Such discipline is known to be friendly to inference and has be used in many
contexts, including OCaml itself, and has been combined
with constraints~\citet{DBLP:journals/tapos/OderskySW99,DBLP:conf/sas/TrifonovS96}.
In particular, Flowcaml~\citep{DBLP:conf/popl/PottierS02}
extends OCaml with security levels forming a lattice and supports type inference.
In \lang, we repurpose these ideas to check for linearity and affinity.
\citet{DBLP:conf/aplas/Simonet03} also presents various algorithmic
notions to solve lattice-based constraints, which we partially use
in our constraint solving algorithm. Our main contribution
is the design of a kind language specialized for checking linearity
and sufficient simple to make
all simplification rules complete, which allows to keep our type signature simple.

>>>>

@@

\subsection{Substructural type-system in functional languages}

@@

\subsection{Other substructural systems}

Linear and affine discipline have also been used in non-functional
settings, notably in the context of low-level imperative programming
and object systems. In particular, \lang uses borrows and regions
which were initially developed in objects or
imperatives settings~\citep{DBLP:conf/popl/BoylandR05,DBLP:conf/pldi/GrossmanMJHWC02}.

@@

\lang relies on qualified types~\cite{DBLP:journals/scp/Jones94}
to introduce the necessary kind equalities for linear types. In
particular, we use HM(X)~\citep{DBLP:journals/tapos/OderskySW99} which
allow to use qualified type in an ML-like language with complete
type inference.
HM(X) has been shown to be compatible with subtyping,
bounded universal and existentials~\citep{DBLP:conf/icfp/Simonet03}
GADTs~\citep{DBLP:journals/toplas/SimonetP07},
and syntactic proof of soundness~\citep{DBLP:journals/entcs/SkalkaP02}.
This makes us confident that the system developed in \lang
could be applied to larger and more complex languages such as OCaml.

The subtyping discipline used in \lang is very similar
to structural subtyping, where the only subtyping (or here, subkinding)
is at the leafs.
Such discipline is known to be friendly to inference and has be used in many
contexts, including OCaml itself, and has been combined
with constraints~\citep{DBLP:journals/tapos/OderskySW99,DBLP:conf/sas/TrifonovS96}.
In particular, Flowcaml~\citep{DBLP:conf/popl/PottierS02}
extends OCaml with security levels forming a lattice and supports type inference.
In \lang, we repurpose these ideas to check for linearity and affinity.
\citet{DBLP:conf/aplas/Simonet03} also presents various algorithmic
notions to solve lattice-based constraints, which we partially use
in our constraint solving algorithm. Our main contribution
is the design of a kind language specialized for checking linearity
and sufficient simple to make
all simplification rules complete, which allows to keep type signatures simple.
